MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-04-10 MAESTROeX_I/algorithm.tex
Add figures in results section

One of the key numerical modules is the ``lateral average'', which computes the average over a 
layer of a Cartesian grid variable onto a one-dimensional radial array.
In planar geometries, this is a straightforward arithmetic average of cells at
a particular height since the radial cell centers are in alignment
with the Cartesian grid cell centers.
However for spherical problems, the procedure is much more complicated.
In Section 4 of Paper V, we describe how there is a finite, easily computable set of radii that any Cartesian cell-center can map to.  
Specifically, for every Cartesian cell, there exists an integer $m$ such that the radius to the center of the star is given by $\hat{r}_m=\Delta x\sqrt{0.75+2m}$.
We average by binning all the cells associated with each radii and taking the average.
Then we interpolate this data onto a one-dimensional radial array.  Previously, MAESTRO only allowed for radial arrays with a constant $\Delta r$ (typically equal to $\Delta x/5$.
Here we present a new option to retain an irregularly-spaced radial array to eliminate mapping errors back onto the Cartesian grid state.
Consider a spherical star in hydrostatic equlibrium at rest.  In the absense of reactions, the star should remain at rest.
The buoyancy forcing term in the momentum equation contains $\rho-\rho_0$.  With the original scheme, interpolation errors in computing $\rho_0$ by averaging would cause artifical acceleration in the velocity field due to the interpolation error from the Cartesian grid to and from the radial base state.  By retaining the radial base state as an irregularly spaced array, the effects due to interpolation error are completely eliminated.

>>>>

One of the key numerical modules is the ``lateral average'', which computes the average over a 
layer of a Cartesian grid variable onto a one-dimensional radial array.
In planar geometries, this is a straightforward arithmetic average of cells at
a particular height since the radial cell centers are in alignment
with the Cartesian grid cell centers.
However for spherical problems, the procedure is much more complicated.
In Section 4 of Paper V, we describe how there is a finite, easily computable set of radii that any Cartesian cell-center can map to.  
Specifically, for every Cartesian cell, there exists an integer $m$ such that the radius to the center of the star is given by $\hat{r}_m=\Delta x\sqrt{0.75+2m}$.
We average by binning all the cells associated with each radii and taking the average.
Then we interpolate this data onto a one-dimensional radial array.  Previously, MAESTRO only allowed for radial arrays with a constant $\Delta r$ (typically equal to $\Delta x/5$).
Here we present a new option to retain an irregularly-spaced radial array to eliminate mapping errors back onto the Cartesian grid state.
Consider a spherical star in hydrostatic equlibrium at rest.  In the absense of reactions, the star should remain at rest.
The buoyancy forcing term in the momentum equation contains $\rho-\rho_0$.  With the original scheme, interpolation errors in computing $\rho_0$ by averaging would cause artificial acceleration in the velocity field due to the interpolation error from the Cartesian grid to and from the radial base state.  By retaining the radial base state as an irregularly spaced array, the effects due to interpolation error are completely eliminated.

### 2019-04-10 MAESTROeX_I/results.tex
Add figures in results section

\subsection{AMR Performance}
Show 3D reacting bubble rise performance.
Show 3-level spherical performance (stats won't be as good but explain why: refining a larger percentage of grid)
Images of grid configuration.

>>>>

\subsection{AMR Performance}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=2.75in]{./figs/reacting_bubble_amr} 
$\qquad$
\includegraphics[width=2.75in]{./figs/wdconvect_amr_3grid}
\caption{\label{fig:amr_grids} Initial grid structures with two levels of refinement. 
         The red, green, and black lines represent grids of increasing refinement. 
         (Left) Profile of $T - \bar{T}$ for a hot bubble in a white dwarf environment.
         (Right) Region of star where $\rho\ge 10^5 \text{ g cm}^{-3}$ in a full white dwarf star simulation. }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=2.75in]{./figs/reacting_bubble_result} 
$\qquad$
\includegraphics[width=2.75in]{./figs/reacting_bubble_amr_result}
\caption{\label{fig:bubble_results} Time-lapse cross-section of a hot bubble in a white dwarf environment at 
         $t = 0$, 1.25, and 2.5 s for (left) single-level simulation, and 
         (right) adaptive simulation at the same effective resolution.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
